---
title: "REU_R_2018_workshop_3"
author: "Ilya"
date: "7/2/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#####read in data
```{r read_pantheria}
#####read in PanTHERIA data (source: http://esapubs.org/archive/ecol/e090/184/#data) 
P <- read.csv("PanTHERIA_1-0_WR05_Aug2008.csv", header=TRUE)
```

#####replace -999 with NA
```{r}
#replace
P = replace(P, P==-999, NA)
```

#####plot continuous data as scatterplot
```{r}
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g)
```

#####plot customization: add axis titles
```{r}
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g, 
     xlab = "Dispersal age (days)",
     ylab = "Adult body mass (g)")
```

#####plot customization: log scale
```{r}
#this Stack Overflow thread goes over how to change how numbers appear; one option is to change options(scipen=X)
#https://stackoverflow.com/questions/5963047/do-not-want-scientific-notation-on-plot-axis
options(scipen=5)
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g, 
     xlab = "Dispersal age (days)",
     ylab = "Adult body mass (g)",
     log = "xy")
```


#####plot customization: log scale
```{r}
options(scipen=5)#change scientific to decimal
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g, 
     xlab = "Dispersal age (days)",
     ylab = "Adult body mass (g)",
     log = "xy",
     col = "red")
```

#####plot customization: add title using "main"
```{r}
options(scipen=5)#change scientific to decimal
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g, 
     xlab = "Dispersal age (days)",
     ylab = "Adult body mass (g)",
     log = "xy",
     col = "red",
     main = "Relationship between dispersal age and body mass")
```

#####plot customization: change shape and size of points
```{r}
options(scipen=5)#change scientific to decimal
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g, 
     xlab = "Dispersal age (days)",
     ylab = "Adult body mass (g)",
     log = "xy",
     col = "red", pch = 17, cex = 1.5,#pch: shape; cex: size
     main = "Relationship between dispersal age and body mass")
```

#####plot customization: multiple plots per window
```{r}
options(scipen=5)#change scientific to decimal
# specify (n.rows, n.columns)
par(mfrow = c(1, 2))  #one row, two columns
plot(P$X7.1_DispersalAge_d, P$X5.1_AdultBodyMass_g, 
     xlab = "Dispersal age (days)",ylab = "Adult body mass (g)",
     log = "xy", col = "red", pch = 17, cex = 1.5,#pch: shape; cex: size
     main = "Relationship between dispersal age and body mass")
plot(P$X5.1_AdultBodyMass_g, P$X7.1_DispersalAge_d, 
     ylab = "Dispersal age (days)", xlab = "Adult body mass (g)",
     log = "xy", col = "blue", pch = 17, cex = 1.5,#pch: shape; cex: size
     main = "Relationship between dispersal age and body mass")

```

####Statistical analysis: linear regression
```{r}
my.model.ord.int <- lm(log(X5.1_AdultBodyMass_g) ~ log(X7.1_DispersalAge_d)*MSW05_Order, data = P)
summary(my.model.ord.int)

my.model <- lm(log(X5.1_AdultBodyMass_g) ~ log(X7.1_DispersalAge_d), data = P)
summary(my.model)

```

#####Add line representing linear model
```{r}
# don't forget to reset your graphical parameters
par(mfrow = c(1, 1))

plot(log(P$X7.1_DispersalAge_d), log(P$X5.1_AdultBodyMass_g), 
     xlab = "Dispersal age (days)",ylab = "Adult body mass (g)",
     col = "red", pch = 17, cex = 1.5,#pch: shape; cex: size
     main = "Relationship between dispersal age and body mass")

# adds a line over the scatterplot
abline(my.model,
       log="xy")

# adds text at location (x,y) on plot
text(1000, 100, labels = "R-squared = 0.02349")
text(1000, 20, labels = "p-value = 0.0686")
```

